\documentclass[10pt, letterpaper]{article}
\usepackage[
    pdftitle={Andre Mossi CV (EN)},
    pdfauthor={Andre Mossi},
    pdfcreator={LaTeX and NeoVim}
]{hyperref}

\usepackage{geometry}
\geometry{
    a4paper,
    left=12.7mm,
    right=12.7mm,
    top=12.7mm,
    bottom=12.7mm
}

\usepackage{titlesec}
\titlespacing{\section} {0pt}{-0.1cm}{0cm}
\titlespacing{\subsection} {0pt}{-0.3cm}{0cm}

\pagestyle{empty}

\begin{document}

\begin{center}
    \textbf{\huge{Roberto (Andre) Mossi Milla}}\\

    \vspace{0.3cm}

    \small{
        Erie, Pennsylvania, 16506\\
        \href{tel:+18147901591}{814-790-1591}\\
        \href{mailto:mossiroberto0392@gmail.com}{mossiroberto0392@gmail.com}\\
        \href{https://andremossi-linktree.vercel.app/}{andremossi-linktree.vercel.app}
    }
    \vspace{0.5cm}
\end{center}

\begin{Form}
    \textbf{\section*{SUMMARY}}
    \normalsize{
        Full-Stack developer studying for a B.S. In Computer Science. Developed side projects,
        took online classes, and studied at Gannon University with the goal of increasing my knowledge.
    }

    \textbf{\section*{WORK EXPERIENCE}}

    \textbf{\subsection*{Dinant, Tegucigalpa, Honduras}}

    \subsubsection*{Full-Stack Developer, June-July 2023}
    \begin{itemize}
        \item
            Managed databases of thousands of clients’ using SQL, and created an app to visualize and interact
            with the data. Out of the many databases, one of them was meant to keep track and find assistance with
            ease, if needed, of all the machinery details like current conditions of the various companies
            equipment’s we worked with. Another database that I worked with, was used for keeping information
            of products purchase, status, and type of plan as to have a faster and effective interaction with
            the clients.

        \item
            Created web apps utilizing Apex Oracle, JavaScript, CSS, and some HTML for business clients that are
            prominent latino sellers. The purpose of one of them was to generate digital contracts with easiness
            by updating in real time possible answers in the required filling fields as the user makes choices and
            based on users’ permissions. Another one was an assistance app meant for factory workers we were
            affiliated with to ask for help. Based on the users profile and filled up fields, the program will
            determine the best possible helpers they may need for their necessities.

    \end{itemize}

    \textbf{\subsection*{Gannon University, Pennsylvania, United States}}

    \subsubsection*{Research Assistant, Present}
    \begin{itemize}
        \item
            Working with a professor to develop a research about simulation of organisms meant to emphasize the
            natural selection under environmental constrains.

        \item
            With the use of technologies like python, Cuda, and Pytorch, worked on bringing organisms to life with
            artificial intelligence to study their behavior under a survival assignment, in this case a game of tag.
    \end{itemize}

    \subsubsection*{Student Technician, August - December 2022}
    \begin{itemize}
        \item
            Worked at the IT department of the university. Was responsible for giving assistance in technology related
            issues to students and professors 5 days a week.
    \end{itemize}

    \textbf{\subsection*{Yakiniku Byakutan, Tokyo, Japan}}

    \subsubsection*{Staff, December 2022}
    \begin{itemize}
        \item
            kitchen assistant. Was responsible for making sure that the cleanliness of the restaurant was on par with
            the health registry standards.
    \end{itemize}

    \textbf{\section*{EDUCATION}}

    \textbf{\subsection*{Gannon University, Pennsylvania, United States}}
    Bachelor of Science in Computer Systems Engineering, Present

    \textbf{\subsection*{Harvard University, Online}}
    CS50’s Introduction to Computer Science, December 2022

    \textbf{\subsection*{Extreme Networks, Online}}
    Introduction to Future Networks, May 2022

    \textbf{\section*{ADDITIONAL SKILLS}}
    \begin{itemize}
        \item Proficient in PowerShell, Bash, and NVIM.

        \item
            Learned React, Next.js, Vite, and Vercel for the deployment and development of my portfolio and link
            tree website.

        \item Intermediate level of C++.

        \item
            Learned Linux and made a rice Linux setup with the purpose of increasing my knowledge regarding Operating
            Systems, understanding how a machine works, and being able to read other people’s code.

        \item Written and oral fluency in Spanish.

        \item Written and oral fluency in English

    \end{itemize}

    \textbf{\section*{QUALIFICATIONS SUMMARY}}

    \begin{itemize}
        \item 3 years of experience in Windows PowerShell.

        \item 3 years of experience making games in Unreal Engine.

        \item 1 year of experience debugging software using Visual Studio, IntelliJ, NVIM, and VSCode.

        \item 1 year of experience developing software in C++.

        \item 5 months of experience developing web apps in JavaScript, HTML, and CSS.

        \item 3 months of experience developing software in Java.

        \item 3 months of experience developing software in C\# and C.

        \item 2 months of experience developing large scale cloud services.

        \item 2 months of experience working with Oracle and Oracle Apex.

        \item 2 months of experience developing websites in NodeJS, React, and Next.js.

        \item 3 months of experience developing software in Python.
    \end{itemize}

    \textbf{\section*{AWARDS AND HONORS}}

    \begin{itemize}
        \item "School Development Award" award obtained for outstanding development of a videogame using Blueprints in Unreal Engine 4¸2020.

        \item "School Development Award" award obtained for outstanding development of a videogame using C++ and Unreal Engine 4¸2016.
    \end{itemize}


\end{Form}
\end{document}
